---
title: "Descriptives"
---

```{r, echo=FALSE, include=FALSE}
library(psych)
load(file="../processed_data/preQ.pact.dat.RData")
load(file="../processed_data/sliced.dat.wide.RData")
load(file="../processed_data/postQ.dat.RData")
```

## Implicit Motives

::: {.panel-tabset}

### Implicit Agency motive

```{r, echo=FALSE}
hist(preQ.pact.dat$Agency, col = "darkblue", xlab = "Implicit Agency motive", main = "")
describe(preQ.pact.dat$Agency)
```

### Implicit Power Agency motive

```{r, echo=FALSE}
hist(preQ.pact.dat$AgencyPow, col = "darkblue", xlab = "Implicit Power Agency motive", main = "")
describe(preQ.pact.dat$AgencyPow)
```

### Implicit Independence Agency motive

```{r, echo=FALSE}
hist(preQ.pact.dat$AgencyInd, col = "darkblue", xlab = "Implicit Independence Agency motive", main = "")
describe(preQ.pact.dat$AgencyInd)
```

### Implicit Communion motive

```{r, echo=FALSE}
hist(preQ.pact.dat$Communion, col = "darkblue", xlab = "Implicit Communion motive", main = "")
describe(preQ.pact.dat$Communion)
```

:::

## Relationship satisfaction (RS)

::: {.panel-tabset}

### Couple Satisfaction index

```{r, echo=FALSE}
hist(preQ.pact.dat$csi, col = "darkblue", xlab = "Couple Satisfaction index", main = "")
describe(preQ.pact.dat$csi)
```

### Positive relationship quality

```{r, echo=FALSE}
hist(preQ.pact.dat$prq, col = "darkblue", xlab = "Positive relationship quality", main = "")
describe(preQ.pact.dat$prq)
```

### Negative relationship quality

```{r, echo=FALSE}
hist(preQ.pact.dat$nrq, col = "darkblue", xlab = "Negative relationship quality", main = "")
describe(preQ.pact.dat$nrq)
```

### BZ3 mean (ESM RS mood item)

```{r, echo=FALSE}
hist(sliced.dat.wide$BZ3.mean, col = "darkblue", xlab = "BZ3 mean", main = "")
describe(sliced.dat.wide$BZ3.mean)
```

### BZ4 mean (reversed) (ESM RS annoyance item)

```{r, echo=FALSE}
hist(sliced.dat.wide$BZ4.r.mean, col = "darkblue", xlab = "BZ4 mean (reversed)", main = "")
describe(sliced.dat.wide$BZ4.r.mean)
```

### BZ mean (ESM RS scale)

```{r, echo=FALSE}
hist(sliced.dat.wide$BZ.mean, col = "darkblue", xlab = "BZ mean", main = "")
describe(sliced.dat.wide$BZ.mean)
```

### Retrospective relationship satisfaction (postQ)

```{r, echo=FALSE}
hist(postQ.dat$bz.fb, col = "darkblue", xlab = "Retro BZ", main = "")
describe(postQ.dat$bz.fb)
```

:::