---
title: "Exploration"
---

```{r, echo=FALSE, include=FALSE}
source("../general_analyses/analyses-hyp1.R")
source("../general_analyses/analyses-hyp1-exp.R")
source("../general_analyses/analyses-hyp1-inkrementell.R")
source("../general_analyses/analyses-hyp1-apim-z.R")
```

## Model with Agency and Communion

::: panel-tabset
### CSI

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.csi.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.csi.main)
resfit.H1.csi.main
qqnorm(resid(H1.csi.main))
qqline(resid(H1.csi.main))
```
:::

### PRQ

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.prq.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.prq.main)
resfit.H1.prq.main
qqnorm(resid(H1.prq.main))
qqline(resid(H1.prq.main))
```
:::

### NRQ

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.nrq.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.nrq.main)
resfit.H1.nrq.main
qqnorm(resid(H1.nrq.main))
qqline(resid(H1.nrq.main))
```
:::
:::

## Agency: Incremental effects of explicit and implicit motives

::: {.panel-tabset}

### CSI

```{r, echo=FALSE}
summary(H1.csi.A.ink)
```

### PRQ

```{r, echo=FALSE}
summary(H1.prq.A.ink)
```

### NRQ

```{r, echo=FALSE}
summary(H1.nrq.A.ink)
```

### Correlation explicit and implicit motives

```{r, echo=FALSE}
summary(corr.A.ex.imp)
```

::: 

## Communion: Incremental effects of explicit and implicit motives

::: panel-tabset

### CSI

```{r, echo=FALSE}
summary(H1.csi.C.ink)
```

### PRQ

```{r, echo=FALSE}
summary(H1.prq.C.ink)
```

### NRQ

```{r, echo=FALSE}
summary(H1.nrq.C.ink)
```

### Correlation explicit and implicit motives

```{r, echo=FALSE}
summary(corr.C.ex.imp)
```

:::

## Are individuals' implicit communion motives (trait) positively related to individuals' ...

::: panel-tabset
### ...mean BZ3 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ3.C.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ3.C.main)
resfit.H1.BZ3.C.main
qqnorm(resid(H1.BZ3.C.main))
qqline(resid(H1.BZ3.C.main))
```
:::

### ...mean BZ4 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ4.C.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ4.C.main)
resfit.H1.BZ4.C.main
qqnorm(resid(H1.BZ4.C.main))
qqline(resid(H1.BZ4.C.main))
```
:::

### ...mean BZ state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ.C.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ.C.main)
resfit.H1.BZ.C.main
qqnorm(resid(H1.BZ.C.main))
qqline(resid(H1.BZ.C.main))
```
:::

### ...retrospective assessment of BZ3?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.bz.fb.C.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.bz.fb.C.main)
resfit.H1.bz.fb.C.main
qqnorm(resid(H1.bz.fb.C.main))
qqline(resid(H1.bz.fb.C.main))
```
:::
:::

## Are individuals' implicit agency motives (trait) negatively related to individuals' ...

::: panel-tabset
### ...mean BZ3 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ3.A.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ3.A.main)
resfit.H1.BZ3.A.main
qqnorm(resid(H1.BZ3.A.main))
qqline(resid(H1.BZ3.A.main))
```
:::

### ...mean BZ4 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ4.A.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ4.A.main)
resfit.H1.BZ4.A.main
qqnorm(resid(H1.BZ4.A.main))
qqline(resid(H1.BZ4.A.main))
```
:::

### ...mean BZ state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ.A.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ.A.main)
resfit.H1.BZ.A.main
qqnorm(resid(H1.BZ.A.main))
qqline(resid(H1.BZ.A.main))
```
:::

### ...retrospective assessment of BZ3?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.bz.fb.A.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.bz.fb.A.main)
resfit.H1.bz.fb.A.main
qqnorm(resid(H1.bz.fb.A.main))
qqline(resid(H1.bz.fb.A.main))
```
:::
:::

## Are individuals' implicit agency power motives (trait) negatively related to individuals' ...

::: panel-tabset
### ...CSI?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.csi.A.Pow.main)
```
:::

### ...PRQ?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.prq.A.Pow.main)
```
:::

### ...NRQ

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.nrq.A.Pow.main)
```
:::

### ...mean BZ3 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ3.APsy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ3.APsy.main)
resfit.H1.BZ3.APsy.main
qqnorm(resid(H1.BZ3.APsy.main))
qqline(resid(H1.BZ3.APsy.main))
```
:::

### ...mean BZ4 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ4.APsy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ4.APsy.main)
resfit.H1.BZ4.APsy.main
qqnorm(resid(H1.BZ4.APsy.main))
qqline(resid(H1.BZ4.APsy.main))
```
:::

### ...mean BZ state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ.APsy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ.APsy.main)
resfit.H1.BZ.APsy.main
qqnorm(resid(H1.BZ.APsy.main))
qqline(resid(H1.BZ.APsy.main))
```
:::

### ...retrospective assessment of BZ3?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.bz.fb.APsy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.bz.fb.APsy.main)
resfit.H1.bz.fb.APsy.main
qqnorm(resid(H1.bz.fb.APsy.main))
qqline(resid(H1.bz.fb.APsy.main))
```
:::
:::

## Are individuals' implicit agency independence motives (trait) negatively related to individuals' ...

::: panel-tabset
### ...CSI?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.csi.A.Ind.main)
```
:::

### ...PRQ?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.prq.A.Ind.main)
```
:::

### ...NRQ?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.nrq.A.Ind.main)
```
:::

### ...mean BZ3 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ3.APhy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ3.APhy.main)
resfit.H1.BZ3.APhy.main
qqnorm(resid(H1.BZ3.APhy.main))
qqline(resid(H1.BZ3.APhy.main))
```
:::

### ...mean BZ4 state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ4.APhy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ4.APhy.main)
resfit.H1.BZ4.APhy.main
qqnorm(resid(H1.BZ4.APhy.main))
qqline(resid(H1.BZ4.APhy.main))
```
:::

### ...mean BZ state?

::: panel-tabset
#### Main model

```{r, echo=FALSE}
summary(H1.BZ.APhy.main)
```

#### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.BZ.APhy.main)
resfit.H1.BZ.APhy.main
qqnorm(resid(H1.BZ.APhy.main))
qqline(resid(H1.BZ.APhy.main))
```
:::

### ...retrospective assessment of BZ3?

::: panel-tabset
##### Main model

```{r, echo=FALSE}
summary(H1.bz.fb.APhy.main)
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.bz.fb.APhy.main)
resfit.H1.bz.fb.APhy.main
qqnorm(resid(H1.bz.fb.APhy.main))
qqline(resid(H1.bz.fb.APhy.main))
```
:::
:::

## Communion APIMs

::: panel-tabset
### Simple apims (actor and partner effects without interactions)

::: panel-tabset
#### Main model (constrained, see also preregistered tab)

```{r, echo=FALSE}
summary(H1.apim.C)
```

#### Unconstrained model

```{r, echo=FALSE}
summary(H1.apim.C.uc)
```
:::

### complex apims (actor and partner effects with interactions)

::: panel-tabset
#### Main model (constrained)

```{r, echo=FALSE}
summary(H1.apim.C.int)
```

#### Unconstrained model

```{r, echo=FALSE}
summary(H1.apim.C.uc.int)
```
:::
:::

## Agency APIMs

::: panel-tabset
### Simple apims (actor and partner effects without interactions)

::: panel-tabset
#### Main model (constrained, see also preregistered tab)

```{r, echo=FALSE}
summary(H1.apim.A)
```

#### Unconstrained model

```{r, echo=FALSE}
summary(H1.apim.A.uc)
```
:::

### complex apims (actor and partner effects with interactions)

::: panel-tabset
#### Main model (constrained)

```{r, echo=FALSE}
summary(H1.apim.A.int)
plotRSA(b0 = 0.10, x = -0.247, y = -0.046, xy = -0.292, points = list(value = "predicted", data = dat.hypAPIM.wide[,c("IMot.A.z_m", "IMot.A.z_f", "csi.z_m")]), xlab = "actor's agency", ylab = "partner's agency", zlab = "actor's relationship satisfaction")
```

#### Unconstrained model

```{r, echo=FALSE}
summary(H1.apim.A.uc.int)
```
:::
:::
