---
title: "Preregistered hypotheses"
---

```{r, echo=FALSE, include=FALSE}
source("../general_analyses/analyses-hyp1.R")
```

## Hypothesis 1a: Individuals' implicit agency motives (trait) are negatively related to individuals' relationship satisfaction (trait)

### With partner effects (Actor-Partner-Interdependence Models)

::: {.panel-tabset}

#### CSI

```{r, echo=FALSE}
summary(H1.apim.A)
```

#### PRQ

```{r, echo=FALSE}
summary(H1.apim.A.prq)
```

#### NRQ

```{r, echo=FALSE}
summary(H1.apim.A.nrq)
```

:::

### Without partner effects (Multilevel Models)

::: {.panel-tabset}

#### CSI

::: {.panel-tabset}

##### Main model

```{r, echo=FALSE}
summary(H1.csi.A.main)
```

##### Scatter plot

```{r, echo=FALSE}
H1.csi.A.main.plot
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.csi.A.main)
resfit.H1.csi.A.main
qqnorm(resid(H1.csi.A.main))
qqline(resid(H1.csi.A.main))
```

:::

#### PRQ

::: {.panel-tabset}

##### Main model

```{r, echo=FALSE}
summary(H1.prq.A.main)
```

##### Scatter plot

```{r, echo=FALSE}
H1.prq.A.main.plot
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.prq.A.main)
resfit.H1.prq.A.main
qqnorm(resid(H1.prq.A.main))
qqline(resid(H1.prq.A.main))
```

:::

#### NRQ

::: {.panel-tabset}

##### Main model

```{r, echo=FALSE}
summary(H1.nrq.A.main)
```

##### Scatter plot

```{r, echo=FALSE}
H1.nrq.A.main.plot
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.nrq.A.main)
resfit.H1.nrq.A.main
qqnorm(resid(H1.nrq.A.main))
qqline(resid(H1.nrq.A.main))
```

:::

:::

## Hypothesis 1b: Individuals' implicit communion motives (trait) are positively related to individuals' relationship satisfaction (trait).

### With partner effects (Actor-Partner-Interdependence Models)

::: {.panel-tabset}

#### CSI

```{r, echo=FALSE}
summary(H1.apim.C)
```

#### PRQ

```{r, echo=FALSE}
summary(H1.apim.C.prq)
```

#### NRQ

```{r, echo=FALSE}
summary(H1.apim.C.nrq)
```

:::

### Without partner effects (Multilevel Models)

::: {.panel-tabset}

#### CSI

::: {.panel-tabset}

##### Main model

```{r, echo=FALSE}
summary(H1.csi.C.main)
```

##### Scatter plot

```{r, echo=FALSE}
H1.csi.C.main.plot
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.csi.C.main)
resfit.H1.csi.C.main
qqnorm(resid(H1.csi.C.main))
qqline(resid(H1.csi.C.main))
```

:::

#### PRQ

::: {.panel-tabset}

##### Main model

```{r, echo=FALSE}
summary(H1.prq.C.main)
```

##### Scatter plot

```{r, echo=FALSE}
H1.prq.C.main.plot
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.prq.C.main)
resfit.H1.prq.C.main
qqnorm(resid(H1.prq.C.main))
qqline(resid(H1.prq.C.main))
```

:::

#### NRQ

::: {.panel-tabset}

##### Main model

```{r, echo=FALSE}
summary(H1.nrq.C.main)
```

##### Scatter plot

```{r, echo=FALSE}
H1.nrq.C.main.plot
```

##### icc, residual and qqplot for main model

```{r, echo=FALSE}
performance::icc(H1.nrq.C.main)
resfit.H1.nrq.C.main
qqnorm(resid(H1.nrq.C.main))
qqline(resid(H1.nrq.C.main))
```

:::

:::